%==============================================================
% Abijith G — Academic CV
% ATS-friendly, single-column, max 2 pages
% Compiles on Overleaf with pdfLaTeX
%==============================================================
\documentclass[11pt,letterpaper]{article}

% --- Encoding & fonts (modern, ATS-safe) ---
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}          % clean modern Latin Modern font
\usepackage{microtype}        % better spacing/justification

% --- Layout ---
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{xcolor}

% --- Link styling (subtle, print-friendly) ---
\definecolor{linknavy}{HTML}{1A2B49}
\hypersetup{
  colorlinks=true,
  urlcolor=linknavy,
  linkcolor=linknavy,
  pdftitle={Abijith G - Academic CV},
  pdfauthor={Abijith G}
}

% --- Section formatting ---
\titleformat{\section}
  {\large\bfseries\scshape}
  {}{0em}{}[\vspace{1pt}\titlerule\vspace{2pt}]
\titlespacing*{\section}{0pt}{10pt}{6pt}

% --- List spacing ---
\setlist[itemize]{leftmargin=1.4em, itemsep=1pt, topsep=1pt, parsep=0pt}

% --- No page numbers ---
\pagestyle{empty}

% --- Helper macro for project/entry headers ---
\newcommand{\entry}[3]{%
  \noindent\textbf{#1}\hfill\textbf{#2}\\[1pt]
  \textit{\small #3}\par\vspace{1pt}
}

\setlength{\parindent}{0pt}

%==============================================================
\begin{document}

%-------------------- HEADER --------------------
\begin{center}
  {\LARGE\bfseries\scshape Abijith G}\\[4pt]
  Bangalore, India\\[2pt]
  \href{mailto:reachabijithg@gmail.com}{reachabijithg@gmail.com} \,$\vert$\,
  \href{https://github.com/Riicko-19}{github.com/Riicko-19} \,$\vert$\,
  \href{https://linkedin.com/in/abijith-g-770303296}{linkedin.com/in/abijith-g-770303296}
\end{center}

%-------------------- RESEARCH INTERESTS --------------------
\section{Research Interests}
Agentic AI and multi-agent systems; computer vision and deep learning; multimodal
learning; AI infrastructure and systems; intelligent autonomous agents; AI safety
and transparency.

%-------------------- EDUCATION --------------------
\section{Education}
\entry{Presidency University, Bangalore, India}{Sep 2023 -- May 2027}
{B.Tech, Computer Science Engineering --- Specialization: Artificial Intelligence \& Machine Learning}
\vspace{1pt}
GPA: 8.5 / 10.0
\vspace{4pt}

\entry{St.\ Germains Academy, Bangalore, India}{Aug 2021 -- Feb 2023}
{12th PUC (Higher Secondary Certificate) --- GPA: 8.11}

%-------------------- RESEARCH METHODS --------------------
\section{Research Methods \& Competencies}
\begin{itemize}
  \item \textbf{Experimentation:} ablation studies, transfer learning, systematic
        data augmentation, hyperparameter optimization, benchmarking across
        architecture variants.
  \item \textbf{Modeling:} CNN feature extraction, transformer attention
        architectures, supervised regression and classification, multi-agent
        orchestration.
  \item \textbf{Systems:} reproducible containerized experiment environments,
        autonomous pipeline design, behavioral monitoring and structured trace
        generation.
  \item \textbf{Communication:} technical report writing, methodology
        documentation, open-source release and reproducibility packaging.
\end{itemize}

%-------------------- TECHNICAL SKILLS --------------------
\section{Technical Skills}
\textbf{Programming:} Python, Java, SQL, JavaScript, Node.js\\
\textbf{AI / ML:} PyTorch, TensorFlow, scikit-learn, Transformers, OpenCV, NLTK,
spaCy, OpenAI Gym\\
\textbf{Systems \& Infrastructure:} Docker, Linux, Git, Vercel, Firebase\\
\textbf{Frontend \& Backend:} React, Vite, Express.js, MongoDB, Three.js\\
\textbf{Libraries \& Tools:} pandas, NumPy, Matplotlib, Kaggle, Postman, VS Code

%-------------------- RESEARCH PROJECTS --------------------
\section{Research Projects}

\entry{Transformer-Based Static Sign Language Recognition}{2025}
{Deep Learning $\cdot$ Computer Vision $\cdot$ PyTorch $\cdot$ Transformer Architecture}
\begin{itemize}
  \item Investigated hybrid deep learning architectures combining CNN feature
        extraction with transformer-based attention mechanisms for static sign
        gesture classification.
  \item Designed and evaluated a transfer-learning pipeline on the Kaggle Indian
        Sign Language dataset, reaching 85\% classification accuracy through
        systematic augmentation and hyperparameter optimization.
  \item Conducted ablation studies and benchmarking across architecture variants;
        documented methodology and findings as a formal technical report.
\end{itemize}
\vspace{3pt}

\entry{Seraph --- Orchestrated Multi-Agent Regulatory Intelligence System}{2025}
{Multi-Agent Systems $\cdot$ Agentic AI $\cdot$ Python $\cdot$ React $\cdot$ Cardano IBW Hackathon India --- 4th Place}
\begin{itemize}
  \item Designed and implemented a hierarchical multi-agent system of 12
        specialized AI agents operating across a synchronous layered architecture
        for regulatory compliance automation.
  \item Engineered an autonomous pipeline spanning web-scale information retrieval,
        structured data extraction, policy reconciliation, and file management
        without human-in-the-loop intervention.
  \item Investigated coordination strategies for agent inter-communication and
        task delegation in real-time, dynamic regulatory environments across
        international jurisdictions.
\end{itemize}
\vspace{3pt}

\entry{Sentinel --- AI-Supervised Containerized Development Environment}{2026}
{AI Infrastructure $\cdot$ Agentic AI $\cdot$ Docker $\cdot$ Python $\cdot$ AI Safety}
\begin{itemize}
  \item Designed a Docker-based isolated compute environment for safe, reproducible
        experimentation without risk to host configuration, databases, or local
        file systems.
  \item Implemented automated workspace provisioning and container lifecycle
        management for consistent, disposable development contexts across sessions.
  \item Built an AI-powered behavioral monitoring agent that observes developer
        actions, tool invocations, and agent-initiated operations within the
        sandbox, emitting structured activity reports, execution traces, and safety
        insights.
\end{itemize}
\vspace{3pt}

\entry{MIRA\_C --- Vision-Based Autonomous Fault Diagnosis System}{2025}
{Computer Vision $\cdot$ OpenCV $\cdot$ Regression $\cdot$ Classification $\cdot$ Agentic Detection}
\begin{itemize}
  \item Formulated automotive fault detection as a visual anomaly recognition
        problem using an agent-based architecture that identifies vehicle
        irregularities from real-time image streams.
  \item Integrated OpenCV-based visual perception with supervised regression and
        classification models for multi-class fault categorization and routing to a
        centralized diagnostic unit.
\end{itemize}
\vspace{3pt}

\entry{AbiLang --- Design and Implementation of a Custom Interpreted Language}{2026}
{Programming Language Theory $\cdot$ Compilers $\cdot$ Python $\cdot$ AST $\cdot$ Runtime Systems}
\begin{itemize}
  \item Designed and implemented a fully interpreted language from first
        principles: lexical analysis, recursive-descent parsing, AST construction,
        and runtime evaluation.
  \item Implemented first-class functions, recursion, conditionals, loops, user
        I/O, and a custom error-handling framework.
  \item Developed an interactive REPL, CLI tooling, automated test suites, and
        standalone executable packaging for \texttt{.abi} program deployment.
\end{itemize}

%-------------------- TECHNICAL REPORTS --------------------
\section{Technical Reports}
\begin{itemize}
  \item \textit{Hybrid CNN--Transformer Architectures for Static Sign Language
        Recognition.} Unpublished technical report, 2025. (Self-authored project
        report; not peer-reviewed.)
\end{itemize}

%-------------------- AWARDS --------------------
\section{Awards \& Achievements}
\begin{itemize}
  \item \textbf{4th Place}, Cardano IBW Hackathon India (2025) --- \textit{Seraph:
        Multi-Agent Regulatory Compliance System}.
  \item \textbf{Winner}, Internal University Hackathons --- Presidency University,
        Bangalore.
\end{itemize}

%-------------------- OPEN SOURCE --------------------
\section{Open Source \& Technical Contributions}
\begin{itemize}
  \item Maintains a public GitHub repository
        (\href{https://github.com/Riicko-19}{github.com/Riicko-19}) with documented
        source for AbiLang, Seraph, Sentinel, and MIRA\_C.
  \item Released AbiLang with CLI tooling, an automated test suite, and executable
        packaging for community use and reproducibility.
  \item Documented Seraph's modular agent architecture for extension and
        integration with additional compliance data sources.
\end{itemize}

%-------------------- CERTIFICATIONS --------------------
\section{Certifications}
\begin{itemize}
  \item Python Programming --- Scaler Topics
  \item JavaScript Programming --- LetsUpgrade
  \item MongoDB Bootcamp --- LetsUpgrade
  \item Node.js Bootcamp --- LetsUpgrade
\end{itemize}

\end{document}
